\documentclass{article}

\begin{document}
	\section{Introduction}
	The C programming Language is a low-level programming language ranked among the top two programming languages in the Tiobe index (Tiobe is a project to measure the popularity of a particular programming language by the most searched programming language across web browsers). It is at times referred to as the mother of all programming languages as it is the basis of many other programming languages.
	\subsection{History and Founder}
	 The C programming Language was developed in the Bell laboratory in 1972 by Dennis Mac-Alistair Ritchie .Dennis Ritchie was an American computer scientist(born Sept 9, 1941 died October 12 2011 of cancer and a heart disease he is considered the creator of the C programming language and with a Ken Thompson created the Unix operating system(multi-user operating system). The C programming language is the basis for Unix. In addition to his research work he wrote multiple books one of which is 'The C programming Language'.
	 \subsubsection{Additional Information}
	 C is highly portable( i.e it is not tied to any particular hardware so can be programmed on any system that supports C ( it is machine independent) and it is used for scripting system applications. 
	 C was developed to overcome the drawbacks of previous languages such as B and BCPL(Basic Combined programming language(the drawbacks include;
	 - B and BCPL could not identify the data types
	 -They expressed everything in machine words
	 \paragraph{C programming}
	 This language is very flexible to use. C is the best option for a system level programming language(A system programming language is a programming language used for system programming ,such languages are designed for writing system software). It used in application, operating systems and embedded system development. In C, the program is divided into various modules. It contains 32 keywords including but not limited to; auto, char, float, extern, case, for, if etc)
	 \end{document}